---
title: "AssignmentB-4"
author: "Jasper Zhao"
output: 
  github_document: default
---
## Option A – Strings and functional programming in R
Reference: I used stopwords: the R package for finding and removing any stop word in the passsage.
Link: https://cran.r-project.org/web/packages/stopwords/

First, let's load the necessary libraries.
```{r}
library(stopwords)
library(tidyverse)
library(janeaustenr)
library(stringr)
library(purrr)
library(testthat)
```

### Exercise 1
Reference: I used stopwords: the R package for finding and removing any stop word in the passsage.
Link: https://cran.r-project.org/web/packages/stopwords/

We will use the text of Jane Austen’s novel "Emma" from package ‘janeaustenr’
```{r}
# Load the English stop words from the stopwords library
stop_words <- stopwords("en")

# Process the words in the Emma
emma_words <- emma %>%
  # Convert every word to lowercase
  str_to_lower() %>%
  # Removes all characters other than lowercase letters spaces and apostrophe 
  # (to prevent separate words such as he's and it's into two words), replacing them with spaces
  str_replace_all("[^a-z\\s']", " ") %>%
  # Split into words
  str_split(" ") %>%                            
  unlist()

# Remove stop words according to the stopwords library, and empty strings
emma_words_filtered <- emma_words %>%
  tibble(word = .) %>%
  filter(!word %in% stop_words, word != "")

# Count word frequencies
word_freq <- emma_words_filtered %>%
  count(word, sort = TRUE)

# Select the top 30 most common words and arrange them according to frequency
top_words <- word_freq %>%
  slice_max(order_by = n, n = 30) %>%
  arrange(n)

# Plot the most common words
ggplot(top_words, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Top 30 Most Common Words in Jane Austen's novel Emma except stop words",
       x = "Words",
       y = "Frequency") +
  theme_minimal()
```
### Exercise 2

My modified rules to Pig Latin is:

- For words begin with a consonant sound, the initial consonant of the word is moved to the end.
- For words begin with a vowel sound, the first letter of the word is moved to the end.
- Add the suffix "eh" directly to the end of the rearranged word.

#### The function
```{r}
#' Convert Words to Modified Pig Latin
#'
#' This function converts words into a modified version of Pig Latin. The conversion rule is defined as follow:
#'
#' - For words begin with a consonant sound, the initial consonant of the word is moved to the end.
#' - For words begin with a vowel sound, the first letter of the word is moved to the end.
#' - Add the suffix "eh" directly to the end of the rearranged word.
#'
#' @param words A character vector of words to be converted to modified Pig Latin.
#'
#' @return A character vector of words converted into the modified Pig Latin.
#'
#' @examples
#' convert_to_pig_latin(c("string", "apple", "banana", "orange", "hello"))
#' # Returns: "ingstreh", "ppleaeh", "ananabeh", "rangeoeh", "elloheh"

convert_to_pig_latin <- function(words) {
  # Define vowels
  vowels <- c("a", "e", "i", "o", "u", "A", "E", "I", "O", "U")
  
  # Input validation
  if (!is.character(words)) {
    stop("Input 'words' must be a character vector.")
  }
  
  if (any(str_detect(words, "[^A-Za-z]"))) {
    stop("All elements in 'words' must contain only alphabetic characters.")
  }
  
  # Helper function to process each word in the input words vector
  process_word <- function(word) {
    # Check if the word starts with a vowel
    starts_with_vowel <- str_sub(word, 1, 1) %in% vowels
    
    if (starts_with_vowel) {
      # Word start with vowel: Move the first letter to the end
      if (str_length(word) == 1) {
        rearranged <- word
      } else {
        rearranged <- str_c(str_sub(word, 2, -1), str_sub(word, 1, 1))
      }
    } else {
      # Word start with consonant: Move the initial consonant cluster to the end
      
      # Find the position of the first vowel
      first_vowel_pos <- str_locate(word, "[AEIOUaeiou]")[1]
      
      if (is.na(first_vowel_pos)) {
        # No vowels in the word, treat the entire word as consonant cluster
        rearranged <- word
      } else {
        if (first_vowel_pos == 1) {
          rearranged <- word
        } else {
          consonant_cluster <- str_sub(word, 1, first_vowel_pos - 1)
          rest_of_word <- str_sub(word, first_vowel_pos, -1)
          rearranged <- str_c(rest_of_word, consonant_cluster)
        }
      }
    }
    
    # Add "eh" to the rearranged word and return it
    return(str_c(rearranged, "eh"))
  }
  
  # Apply the helper function to all words
  pig_latin_words <- map_chr(words, process_word)
  
  return(pig_latin_words)
}
```

#### Usage Examples
```{r}
words_a <- c("string", "apple", "banana", "orange", "hello")
convert_to_pig_latin(words_a)
```

```{r}
words_b <- c("UBC", "Holy")
convert_to_pig_latin(words_b)
```
#### Unite Tests
Test 1: The function can handle consonant-start words correctly
```{r}
# Unit Tests
test_that("Function handles consonant-start words correctly", {
  expect_equal(convert_to_pig_latin("string"), "ingstreh")
  expect_equal(convert_to_pig_latin("hello"), "elloheh")
})
```

Test 2: The function can handle vowel-start words correctly
```{r}
test_that("Function handles vowel-start words correctly", {
  expect_equal(convert_to_pig_latin("apple"), "ppleaeh")
  expect_equal(convert_to_pig_latin("orange"), "rangeoeh")
})
```

Test 3: The function can handle single-letter words correctly
```{r}
test_that("Function handles single-letter words correctly", {
  expect_equal(convert_to_pig_latin("a"), "aeh")
  expect_equal(convert_to_pig_latin("b"), "beh")
})
```

Test 4: The function can throw error for non-character inputs
```{r}
test_that("Function throws error for non-character inputs", {
  expect_error(convert_to_pig_latin(123), "Input 'words' must be a character vector.")
  expect_error(convert_to_pig_latin(TRUE), "Input 'words' must be a character vector.")
})
```

Test 5: The function can throw error for words with non-alphabetic characters
```{r}
test_that("Function throws error for words with non-alphabetic characters", {
  expect_error(convert_to_pig_latin("hello!"), "All elements in 'words' must contain only alphabetic characters.")
  expect_error(convert_to_pig_latin("good-day"), "All elements in 'words' must contain only alphabetic characters.")
 })
```

